---
title: "Appendix C"
output: html_notebook
---

Data cleaning for RNN training.

```{r}
library(tidyverse)
library(ggplot2)
raw <- read.csv("D:\\5291_data\\5291.csv", encoding="UTF-8")
head(raw)
```

Revenue data is in string format, change it to float number.
```{r}
to_num_revenue <- function(x){
  s <- str_replace_all(x, c("\\$"="", "," = "" ))
  return(as.numeric(s))
}

# baby_raw is a reduced dataframe
baby_raw = raw%>%
  select(Statement.Month,Release.Name, Net.Revenue.USD)%>%
  mutate(Net.Revenue.USD_num =  to_num_revenue(Net.Revenue.USD))%>%
  select(-Net.Revenue.USD)%>%
  group_by(Statement.Month,Release.Name)%>%
  summarise(Net.Revenue.USD_sum = sum(Net.Revenue.USD_num))

name_month_revenue <- baby_raw%>%
  pivot_wider(names_from = Release.Name,values_from = Net.Revenue.USD_sum)%>%
  arrange(Statement.Month)

name_month_revenue[is.na(name_month_revenue)] <- 0

ggplot(data =baby_raw) + 
  geom_point(mapping = aes(x = Statement.Month, y = Net.Revenue.USD_sum))

```
We get 44*255 dataframe, representing 44 months and 255 songs. Now, writing two dataframes to csv files for later use in jupyter notebook.
```{r}
revenue_by_month <- name_month_revenue%>%
  select(Statement.Month)
revenue_by_month$average_revenue <- rowSums(name_month_revenue[,c(2:44)])

### write to csv
readr::write_csv(revenue_by_month, "output/revenue_by_month.csv")
readr::write_csv(name_month_revenue, "output/name_month_revenue.csv")

```

Finally, lets take a look at popular songs. We define popular songs by songs whose revenue is over 12500$ in a single month. Only four songs satisfy the definition.
```{r}
popular_song <- baby_raw%>%
  filter(Net.Revenue.USD_sum>=12500)
unique(popular_song$Release.Name)
```



